\section{Introduction (1 page)}

Android marketshare, numbers, importance. 
Briefly explaing that Android applications interact through intents and ICC

Discuss past analysis, how they often are built for soundness, and therefore suffer on scalability. Also mention about trying to capture each and every way of building intents and ICC

Explain that intents and ICC are built following patterns. Use a small
example?\marcelo{Yes, please.  This is very very important.  You can
  have one super-short simple-to-describe example here and have a
  section of example(s) following this intro section.} We can explore this to create lightweight analysis, that are imprecise, but can account for most of the scenarios, as we show in the evaluation (hopefully). 

Brief idea of the solution. 

We make the following contributions:
\begin{itemize}
 \item~\textbf{Idea.} We leverage the idea of overlapping analysis information to
   reduce cost of static analyses.\marcelo{check if this is really
     new.  Highlight how this embraces the philosophy of soundiness.}
 \item~\textbf{Implementation.} We implemented a tool for computing Android ICC in a
   pattern-based way\marcelo{Think about a good name.  Maybe PBICC is
     not the best.  Use a latex macro as placeholder.};
 \item~\textbf{Evaluation.} We perform a study with $XX$ applications, comparing the results with the state-of-the-art analysis for detecting ICC~\cite{epicc,iccta,comdroid}
 \item something about client analysis here? \emph{We analyze the
   impact that our solution has on tools that perform taint analysis
   on Android applications...}\marcelo{I think these 2 bullets should
   be combined.}
\end{itemize}


